
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Yuriy V. Yakovlev -- Resume} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> ul. Mira 29A 125,\\ % Address line 1
\> Saratov, 410033 \\ % Address line 2
{\bf Date of Birth} \> 21$^{th}$ April 1988 \\ % Date of birth 
{\bf Nationality} \> Russian % Nationality
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Home Phone} \> +7 (964) 848 3479 \\ % Home phone
{\bf Mobile Phone} \> +7 (937) 803 8701 \\ % Mobile phone
{\bf Email} \> \href{mailto:krotos139@gmail.com}{krotos139@gmail.com} \\ % Email address
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

%\section{Personal Profile}
%
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis elementum nec dolor sed sagittis. Cras justo lorem, volutpat mattis lacus vel, consequat aliquam quam. Interdum et malesuada fames ac ante ipsum primis in faucibus. Integer blandit, massa at tincidunt ornare, dolor magna interdum felis, ac blandit urna neque in turpis.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{2005-2012} \> Yuri Gagarin State Technical University of Saratov - \href{http://en.sstu.ru}{SSTU} \\[5pt]
\>Departament - School of Electronics and Instrumentation -  \\
\>Chair of computer software systems\\
\>\+
}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{2014 -}{2016}
{OJSC "Saratovsky elektropriborostroitelny plant named after Sergo Ordzhonikidze", 239, Bolshaya Sadovaya Str., Saratov, Saratov Region, 410005}
{http://www.zaprib.ru}
{Technical Team Lead}
{I developed software for aircraft. I was lead of developing software for computer on Freescale P1010 CPU, i.MX6 CPU. I was developed AHCI driver for VxWorks653.\\
\rule{0mm}{5mm}\textbf{Technologies:} C, Python, Latex, Doxygen, Linux, VxWorks653, GIT.}

%------------------------------------------------

\job
{Feb 2012 -}{2016}
{SKTB "SKiT" (Control Systems and Telematics), Bolshaya Sadovaya str. 139, Russia}
{http://www.skitlab.ru/}
{Senior Software Engineer}
{I developed software for aircraft. I developed software for MAVIm(Mezzanine module of ARINC 429, 708, 825), MMPm(Mass storage mezzanine), MGPm(Graphics processor mezzanine) for Linux OS and VxWorks 653 OS for VIM-3U-3(computer on Freescale P1010 CPU). I developed software for testing stand. I used for it Python and PyQT.\\
\rule{0mm}{5mm}\textbf{Technologies:} C, Python, Latex, Doxygen, QT4, GDB, Linux, VxWorks653, GIT.}

%------------------------------------------------

\job
{Mar 2010 -}{Feb 2012}
{OOO "NPO ATS", OOO "Company "ALSiTEC", Bolshaya Kazachia str. 6, Russia}
{http://www.alstec.ru}
{Software Engineer}
{I developed software for telephone station. I developed SNMP server. I tested monitoring system for telephone station.\\
\rule{0mm}{5mm}\textbf{Technologies:} C, QT4, Linux, GIT.}

%------------------------------------------------

\job
{June 2006 -}{April 2010}
{ZAO "NPK PO", prospect 50 let Oktabrya, Saratov, Russia}
{http://okna.bz/site/npkpo/}
{Junior Software Engineer}
{I developed software for industrial automation system. I developed CNC system.\\
\rule{0mm}{5mm}\textbf{Technologies:} C, AVR Asm, Linux.}



%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Software Engineering Skills}

\skillgroup{Programming Languages}
{
\textit{ะก, ะก++, QT}\\
\textit{Python, PyQT}\\
\textit{PHP}\\
\textit{Java}\\
\textit{SQL}
}

%------------------------------------------------

\skillgroup{Embeded System Development}
{
\textit{Linux kernel for PowerPC, ARM}\\
\textit{U-boot for PowerPC, ARM}\\
\textit{Hardware protocols: I2C, SPI, Ethernet, PCI, PCIe}\\
\textit{Experience used CPUs: Freescale P1010, P2020, i.MX6}\\
\textit{Experience used microcontroller: AVR, Freescale, PIC}\\
\textit{Experience debuging bareboard software(initial start uboot and linux kernel)}
}

%------------------------------------------------

\skillgroup{Foreign language}
{
\textit{English - B1}\\
\textit{Technical english - read documentation for theme IT, Hardware.}
}

%------------------------------------------------

\skillgroup{Web Development}
{
\textit{HTML, CSS, JavaScript/jQuery}\\
\textit{Django}\\
\textit{Apache/Nginx Web Servers}
}

%------------------------------------------------

\skillgroup{Miscellaneous}
{
\textit{MySQL Server}\\
\textit{GIT} - Source version control
\textit{Doxygen} - Tool for generating documentation from annotation sources
\textit{Latex} - A Document preparation system

}


%------------------------------------------------

\skillgroup{Documentation}
{
\textit{ESPD - Central System of Programm Documentation. Russian standart "GOST 19"}\\
\textit{DO-178B, DO-178C - Software Considerations in Airborne Systems and Equipment Certification}\\
\textit{ESKD - Central System of design documentation. Russian standart "GOST 2"}
}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%\section{Interests}
%\interestsgroup{
%\interest{Running, Cycling, Sailing}
%\interest{Travelling}
%}

%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

\section{Referees}

\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Pavel I. Nakonechny \\ % Referee name
{\bf Company} \> OOO "SKTB "SKiT" \\ % Referee company
{\bf Position} \> Deputy Director (d'not working now) \\ % Referee job title 
{\bf Contact} \> \href{mailto:zorg1331@gmail.com}{zorg1331@gmail.com} % Referee contact information
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Ilya A. Dementev\\ % Referee name
{\bf Company} \> OOO "SKTB "SKiT" \\ % Referee company
{\bf Position} \> Hardware Developer \\ % Referee job title 
{\bf Contact} \> \href{mailto:ilya.dementev@skitlab.ru}{ilya.dementev@skitlab.ru} % Referee contact information
\end{tabbing}}

%----------------------------------------------------------------------------------------

